Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-11-19 draft.tex
move paragraph on sufficient but not necessary to alternative outcomes section

The restrictions on the class of games in $\mathcal{G}$ are sufficient but not necessary. For example, if the status quo initially has a much higher long term payoff than the next best alternative for the secessionists, Restriction (6) need not be met to maintain the status quo in the short run. The inequality \emph{will} bind for some set of periods $t \geq 1$ because the secessionist payoffs from the status quo decrease over time. In cases where Restriction (6) is not met, we can have unrecognized statehood for some time, but it is not a long-run equilibrium outcome.

@@

The restrictions in Definition 1 \emph{do not} provide for a unique equilibrium, or even a unique equilibrium outcome. In fact, at least one additional equilibrium outcome always coexists with the status quo outcome.

>>>>

@@

First, note that the restrictions in Definition 1 are sufficient but not necessary. For example, if the status quo initially has a much higher long term payoff than the next best alternative for the secessionists, Restriction (6) need not be met to maintain the status quo in the short run. The inequality \emph{will} bind for some set of periods $t \geq 1$ because the secessionist payoffs from the status quo decrease over time. In cases where Restriction (6) is not met, we can have unrecognized statehood for some time, but it is not a long-run equilibrium outcome.

On the other hand, the restrictions in Definition 1 also \emph{do not} provide for a unique equilibrium, or even a unique equilibrium outcome. In fact, at least one additional equilibrium outcome always coexists with the status quo outcome.
